### 2016-01-20 paper.tex
Remove repeated word

Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
mainly see unsteadiness in the flow generated by the blade tip vortex shedding
(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, turbulence
generation is lower overall, without the intense vertical band around $y/R=-1$,
which indicates that the RM2 blades are operating further from
stall---consistent with the higher tip speed ratio operation.

>>>>

Fig.~\ref{fig:kcont} shows the turbulence kinetic energy in the turbine wake. We
mainly see unsteadiness in the flow generated by the blade tip vortex shedding
(the horizontal band around $z/H=0.5$). Compared with the UNH-RVAT, turbulence
generation is lower overall, without the intense vertical band around $y/R=-1$,
which indicates that the RM2 blades are operating further from
stall---consistent with its higher optimal tip speed ratio.
